---
title: "p8105_hw4_jl6648"
output: html_document
date: "2023-10-26"
---

# Welcome to my website 

This is the introduction:

My name is Jixin Li, here is my website. The resume page include a resume with my academic and professional experience, please check it out. The upper right coner shows a link to my email and GitHub account, please feel free to reach out! 

# Here is the next section 

this is a [link](https://github.com/jl6648) to my GitHub account. this is a [link](mailto:<jl6648@cumc.columbia.edu>) to my email. this is a [link](https://www.linkedin.com/feed/?trk=homepage-basic_sign-in-submit) to my linkin. 

## problem 2


```{r setup, include=FALSE}
library(flexdashboard)

library(tidyverse)
library(plotly)
library(p8105.datasets)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
data("rest_inspec")

rest_inspec_df =
  rest_inspec |>
  filter(grade %in% c("A", "B", "C"), boro != "Missing") |> 
  mutate(boro = str_to_title(boro))

rest_inspec_df |>
  drop_na() |>
  ggplot(aes(x = boro, y = score, color = boro)) +
  geom_boxplot(outlier.color = "black")
```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

rest_inspec_df |>
  drop_na() |>
  ggplot(aes(x = inspection_date, y = score, color = boro)) +
  facet_wrap(~boro) +
  geom_line()

```

### Chart C


```{r}

rest_inspec_df |> 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) |>
  mutate(
    boro = fct_infreq(boro),
    boro = fct_recode(boro, "The City" = "Manhattan")) |>
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() 
```

